### 2012-12-07 intention motor representation goal ascription with corrado sinigaglia (paper 2)/Motor Representation in Goal Ascription.tex
updated

The second step in our attempt to understand how some judgements depend on motor representations concerns the apparent isolation of motor representation from thought. When judgements about the goals of observed actions depend on the observers' motor representations, which processes connect motor representations to judgements?
We shall argue (in section \vref{sec:processes} that motor representations are related to experiences.  There is a parallel between visual and motor representations. Visual representations of the particular colours of objects are related to experiences of those objects and their colours, and these experiences arguably provide reasons for judgements about the colours of objects.%
\footnote{
*Some controversy.  Campbell: yes; Davidson: no (experience plays a merely causal role).  We simply assume yes.  (Or we can duck: we're talking about appearance to the thinker of having reasons, not the fact of having reasons.)}
So the fact that visual representations enable judgements about particular colours in no way conflicts with the claim that thinkers have reasons for those judgements.  We shall argue that motor representations of outcomes are related to experiences of actions and their directedness to outcomes.  This is why thinkers can have reasons for judgements about the directedness of an action to a goal even where the judgements are enabled by motor representations---and also why it appears (veridically) to thinkers that they have such reasons.  Motor representation stands to experience of action as visual representation stands to experience of particular colours. This anyway is the view we shall defend.

@@

\section{***Notes for Action Experience section}

DUSSELDORF ARGUMENT (rough, from Friday skype):
(1) Motor imagery involves experience of action as such (e.g. of grasping as such) and not just of sensory consequences of actions
(one relevant consideration is that you know not only which action you are imagining but when you have succeeded in imagining performing it);
(corollary: there can be experiences of action without experiences of acting)
(2) There are common elements between what you  experience when you imagine acting and what sometimes you experience when you observe an action; in particular, the experience of action is common to both
Therefore
(3) Sometimes observing action involves experiencing action as such

------- there is evidence that motor representation might have content-respecting influences on judgment

MR ----?----- JUD
  experience: how to argue 
….............how is possibile? experience revelatory of action
------------------- parallel between colour and action experience

TBE: content-respecting influences of (MR of G$_1$) onto (Jud about G$_2$) where G$_1$ matches G$_2$

Explanation-1: MR of G captures directedness of action a -> experiences of action a as directed to G -> judgement that action is directed to goal G
	Key component: Dusseldorf argument, imagination

Explanation-2: MR of G captures directedness of action a -> experiences revelatory of action but experiences as of sensory consequences of actions -> association between experienced sensory consequences and action directed to goal G (how? for example, I know the sound of a newspaper being opened) -> judgement that action a is directed to goal G

E.g. clapping:
	representation of sound
	representation of action
	association: characteristic sounds<>action
	Thanks to the association, experience of the sounds can result in a representation of the action

\section{Experience of Action}
\label{sec:processes}
Our aim in this section is to explain how motor representations could sometimes have content-respecting influences on judgements about the goals of observed actions. Broadly, our will be proposal is that the influence of motor representation on observational judgements goes via experience.  It is because motor representations can affect our experiences when we observe actions that those motor representations can facilitate judgements about the actions. However this is consistent with two quite different hypotheses concerning the experiences associated with motor representation in action observation.

One hypothesis, call it the Indirect Hypothesis, is based on evidence that, in observing action, motor representation can influence visual and acoustic experience.  (Perhaps this holds for other modalities too).  On this hypothesis, these influences enable an observer to identify goals to which the observed action is directed because the observer is additionally able to recognise actions from their associated sensory effects. To illustrate, suppose that an observer can associate the characteristic sound of a newspaper being snapped open with the action of snapping open a newspaper. Suppose also that, when observing an action, motor representations can influence whether, when or how she experiences this characteristic sound.  Then motor processes can indirectly influence the speed and accuracy of the observer's judgements about which actions are directed to this goal, the snapping open of a newspaper, by influencing whether, when or how she experiences the characteristic sound of this action.%
\footnote{
The Indirect Hypothesis is inspired by and consistent with views defended in \citet{Csibra:2007fy} and *Knoblich.  However, to our knowledge these authors have not considered exactly our question about content-respecting influences of motor representation on judgement, and we are not suggesting that the would endorse the Indirect Hypothesis in its entirety.  
}

The other hypothesis is in some ways more radical.  This hypothesis, call it the Direct Hypothesis, is that in observing action we experience not only movements and sounds but also goal-directed actions as such. Such experiences---call the motor experiences---stand to motor representations roughly as visual experiences stand to visual representations.  The motor experience of an action as directed to a particular outcome is made possible by a motor representation of that outcome.  So motor representations can have a content-respecting influence on judgements because motor representations enable motor experiences on which judgements are based.%
\footnote{
In formulating the Direct Hypothesis we draw on ideas from \citet{rizzolatti_mirrors_2008} and \citet{Jeannerod:1999kj}.
}

Let us say that an experience, motor or not, is revelatory of action just if it  can provide the subject of experience with reasons for correct judgements about which action someone is performing. On both hypotheses motor representations enable experiences which are revelatory of action. And both hypotheses use this broad idea to explain how motor representations could have content-respecting influences on judgements. The primary difference between the hypotheses concerns what these revelatory experiences are experiences of: whether all such are experiences of movements, sounds and the like only (the Indirect Hypothesis), or whether some are experiences of goal-directed actions as such (the Direct Hypothesis).

In the next section we expand on and consider evidence for the first hypothesis before turning to the second hypothesis in the following section.

\section{The Indirect Hypothesis}
The Indirect Hypothesis is depends on the claim that motor representations can influence sensory experiences.  This claim is supported by a variety of evidence.  \citet{bortoletto:2011_action} show that motor plans, such as might be involved in producing a gesture with the hand, can influence visual processes \citep{bortoletto:2011_action}. The influence of motor representations on visual processes varies depending on both the gesture to be performed and the visual stimulus presented. Importantly, these influences can be detected before any action occurs, showing that it is the motor representations rather than any consequent movements which are influencing visual processes. [*Some other evidence; stress that the effect can be found using different measures.]  As it may be possible to influence visual processes in ways that make no difference to experience, we do not take these findings alone to establish the claim that motor representations could enable visual experiences.  But these findings do at least show that the claim is consistent with the neuropsychological facts.% 
\footnote{
For a recent review of some of the evidence concerning motor influences on perceptual processing, see \citet{halasz:2012_unconscious}. (*refs)
}

What would establish that some motor representations enable perceptual experiences? For some very special pairs of tones, the first is sometimes perceived as lower in pitch than the second and sometimes as higher in pitch.  Repp and Knoblich (\citeyear{repp:2007_action}) had a group of expert pianists and a control group of non-experts press two keys in sequence, where the first key was sometimes left and sometimes right of the second key.  They found that, for the expert pianists, the direction of the key presses modulated the experience: it influenced the perceived direction of the change in pitch. Could what modulates experience in this case be not a motor representation but the occurrence of a movement, or perhaps even the perception of a movement of the subject's own fingers?  Against this, note that the effect was not observed in non-expert pianists: for them the direction of action did not measurably influence the experienced pitch direction. Since both groups moved in the same way, if the modulation were due to movement only we would expect it to occur irrespective of expertise. Instead it seems likely that differences in expertise between the two groups of subjects affected how the movements they performed were represented motorically, and these differences in motor representation are in turn what explains their experience of the change in pitch.  This study, and others like it,%
\footnote{
See also \citet{zwickel:2010_interference} who investigate effects of action on visual experience of motion.  *more
} 
provide relatively direct evidence that motor representations can enable acoustic experiences.

How do these findings bear on the second hypothesis above, according to which motor representation in action observation enables experiences of sounds and movements that somehow facilitate the identification of actions?  Perhaps the motor representations enable certain experiences of kinematic features which somehow enable subjects to better identify actions.  We do not claim that this is entirely plausible, only that the second hypothesis cannot be rejected out of hand.  This is enough to show that we cannot infer that there are experiences of action just from the fact that motor representation enables experiences which are revelatory of action.  Stronger evidence for the first hypothesis is needed.

\subsection{Experiences of action}
Our focus is experiences involved in observing actions, but let us first consider experiences involved in performing actions.  We shall argue that acting sometimes involves experiences which can ground judgements about what one has done even though these are not experiences of movements or sounds.  In effect, the idea will be that you can strip away perceptual experiences and still be left with experiences revelatory of action.  These can only be experiences of action, or so we claim.  Two phenomena are involved in making this argument.  The first is anosognosia for hemiplegia, which shows that there can be experiences revelatory of action even in the absence of any actual movements.  The second is deafference, which confirms that these experiences are unlikely to be illusory experiences of movement. Together these phenomena support the view that, in performing actions, we have experiences of actions and not only of movements, sounds and the like.

The argument sketched so far concerns experiences associated with performing actions, not observing them.  Note, however, that the basis of these experiences of action is motor representation and planning.  Since these are the very things which, in action observation, underlie the experiences enabling one to identify actions, it is reasonable to conclude that there is a phenomenal element common to performing an action and observing an action performed, namely the action itself.  Roughly, what you experience in performing an action is what you would experience if you were observing it.  But this is all to come; let us start by introducing some background.

Anosognosia for hemiplegia is a clinical condition in which patients deny, and appear largely unaware of, a severe paralysis of one or more limbs on one side of their body.  It typically follows a stroke involving damage to motor areas in the right hemisphere of the brain (*refs).  To illustrate the effects of this condition, consider a subject with anosognosia for hemiplegia who was asked to brush her hair holding a brush in her contralesional hand.  Although she was unable to move the hand, she proceeded to move her head as if her hair were being brushed, and then reported having successfully brushed her hair \citep{berti:2008_motor}. This form of anosognosia cannot be explained as entirely due to neglect or complete ignorance of part of one's body \citep[p.\ 165]{berti:2008_motor}.

Could anosognosia for hemiplegia be explained as mere  confabulation or a top-down effect of judgement on experience?  This is incompatible with the performance of anosognosics on bimanual tasks \citep{berti:2008_motor, garbarini:2012_moving}.  To illustrate, consider an anosognosic who has been asked to wash with both hands.  Although she can only actually move one hand, she may move this hand in much the way that she would do if she were actually washing with both hands (*ref: personal communication?).  This is hard for ordinary subjects to reproduce (try it). For a more carefully controlled illustration, consider anosognosic subjects who were asked to draw simultaneously with both hands, one hand was supposed to continuously draw a vertical line and the other hand to continuously draws a circle.  Anosognosic subjects can of course only actually move one hand, but they show interference as if both hands were actually being moved.  That is, if you were to perform this task, your vertical line would become somewhat oval; this interference is an effect of bimanual coordination.  The striking finding is that anosognosic subjects show the same pattern of interference although not actually drawing a circle.  By contrast, subjects with motor neglect and subjects with hemiplegia but no anosognosia do not show this pattern of interference \citep{garbarini:2012_moving}.  This suggests that anosognosia involves relatively detailed action-related experiences and cannot be entirely explained as confabulation.

On the leading, best supported explanation, anosognosia for hemiplegia arises from defects in monitoring action.  When a subject with anosognosia for hemiplegia is asked to perform an action involving a hemiparetic limb, motor planning occurs as it might do in ordinary subjects. Now in ordinary subjects, and in hemiplegic subjects without anosognosia, the predicted effects of a planned action are compared with motor representations of action outcomes.  Consequently if such subjects tried and failed to initiate an action, they would normally be aware of their failure even without seeing or touching their limbs. However, in anosognosic subjects the comparator is damaged and no signal of failure is generated.  This is why it seems to them that they have acted despite failing even to initiate the action.  Of course, anosognosic subjects can perceive that their objectives have not been met: after apparently opening a bottle, for instance, they can see that the bottle remains shut; they would not normally proceed to drink from it.  And these subjects do not necessarily have visual, proprioceptive or tactile sensory impairments.  But the experience associated with motor planning dominates, so that it seems to them as if they have acted.  From their point of view, it seems that the bottle is peculiarly difficult to open rather than that they are unable to move a limb \citep[pp.\ 173-4]{berti:2008_motor}.

How is anosognosia for hemiplegia relevant to the issue of whether there are experiences of action as such?  It seems that anosognosic subjects have some experiences which are revelatory of action---revelatory in the sense that they provide reasons for judgements about actions---despite not actually moving a limb.  What could these experiences be experiences of?  Consider the claim that these are experiences of movement only.  While it is arguably not generally correct to infer an absence of experience of movement from the absence of actual movement, in this particular case it does seems unlikely that there could be experience of movement.  After all, some anosognosic subjects have intact perceptual systems: if they experience movement at all, they should experience an absence of movement.  So any experiences of movement will not be the sort of experiences that would provide reasons for judgements about successful action.  Given that (as argued above) the experiences on which anosognosic subjects' judgements of action are based are also not entirely a product of confabulation, it is plausible to accept that they are experiences of action as such.

This view is further supported by research on deafferented subjects.  These subjects lack tactile and proprioceptive sensory feedback from their actions but, unlike subjects with anosognosia for hemiplegia, can actually move their limbs.  Such subjects may continue to have some experiences characteristic of action; for instance, when asked to flex an index finger they can report having done so even in the absence of visual information \citep{kristeva:2006}.  These subjects' sensory deficits make it unlikely that their experiences could be of movements or the like: it is more plausible that, concerning acting, their experiences are like those of subjects with anosognosia for hemiplegia.  None experience movement: what they experience is action.

Anosognosia and deafference comprise a useful pair of cases: some anosognosics we have preserved perceptual senses and an absence of actual bodily movement, whereas individuals suffering deafference have damaged senses and actual bodily movement.  But in both cases there are experiences revelatory of action.  The existence of these disorders indicates that motor representation is sufficient for experiences capable of grounding judgements about actions even in the absence of any perceptual experiences of movements, sounds or the like.  It is plausible to infer that these experiences are experiences of action as such.

***HERE: todo.  Two things.  First, explain the timing experiment---it's not all about subjects with brain damage, there is converging evidence from ordinary subjects.  Second, explain the comparitor model.

***Anosognosia for hemiplegia : experience of action without acting (cannot be an experience of movement, \&c).  Or could this be an illusory experience of one's body moving?  \citep{garbarini:2012_moving}%
\footnote{
See also \citet{gallese:2010_bodily}: "Brugger, Kollias, Muri, Crelier, and Hepp-Reymond (2000) described one of these cases. fMRI imaging of their patient during phantom limb sensations of hand movements showed activation of premotor and posterior parietal cortex. Aplasic phantoms can therefore be explained as the phenomenal correlate of planning/monitoring action of an absent limb."}
and hand-washing: \citep{berti:2008_motor}

***parallel with speech (short)

\section{Conclusion}
Motor representation enables judgements about the goals of actions by making possible experiences of action as such.

\subsection{Reasons}
In making judgements about the goals of actions, it appears (perhaps veridically) to the thinker that she has reasons for those judgements, much as it appears to her that she has when making visual judgements about the particular colours of objects.  Or, if we are sceptical about thinkers having reasons for visual judgements, at least we can say that it does not seem to the thinker that she is simply landed with the judgement.  Contrast someone who `knew at a glance' that a vase is genuine Ding ware, or someone on a blind date who, on first catching sight of her partner for the night, `just knows' that this is the one she wants to spend the rest of her life with.  Action judgements often seem different from these: rather than simply being landed with them, it may seem to a thinker that they bear a straightforward relation to her experience.

Our view is consistent with the claim that it appears to a thinker that she has reasons for making judgements about the goals of actions even when  those judgements depend on motor representations.
  Motor representation stands to experience of action as visual representation stands to experience of particular colours.

\subsection{Goal ascription without metarepresentation}
Having noted above that goal ascription often or always involves representing the directedness of an action to an outcome, we argued that this is something no motor representation can represent. Equally, however, we noted that the directedness of actions to outcomes can be captured by planning-like processes, and we suggested that motor representations can feature in such processes.  One possibility, then, is that there might be a kind of goal ascription---or something resembling goal ascription---where the only representations involved are motor representations.  This enables us to see how there could be goal ascription, or something very like it (we are not insisting that the term 'goal ascription' be used) could occur without metarepresentation. This gives us a first role for motor representation in goal ascription which distinguishes motor representation from representations of intentions or other mental states.  Where goal ascription involves capturing the directedness of actions to goals by representations of intentions it thereby involves metarepresentation; but where the only representations involved in goal ascription are motor representations, there is no metarepresentation at all.

\section{* PLAN *}
[Corrado's Challenge: Why is this not just about implementation details?]
\begin{enumerate}
\item What roles, if any, might motor representation play in goal ascription?
\item Some motor representations occur in action observation and sometimes facilitate goal ascription (Serino; basketball; \& others?) (otherwise the question would be bizarre).  This is what makes the question pressing (timely).
\item The Question: How is this possible?  How could motor representation facilitate goal ascription?
\item Philosophical motivation: A familiar view in philosophy has it that goal ascription depends on the ascription of intentions, which in turn is interdependent with ascriptions of belief and desire (*refs). On this view goal ascription is possible only as part of a larger mindreading project. By contrast, developmental psychologists have assumed that goal ascription is possible even without knowing anything of an agent's mental states (*refs).  Our concern is with this pure form of goal ascription, goal ascription that occurs independently of knowledge of mental states.
\item There are two problems.  (a) adequacy of motor representation; (b) link between motor representation and judgement about the action and its goal
\item Problem (a).  Motor representations may represent outcomes but not the directedness of actions to outcomes?
\item Solution to problem (a): Capturing vs. representing the directedness of actions.
\item Problem (b): If we thought of motor representation as cut off from experience, it would seem impossible that differences in motor representation could make a difference to the reasons available from the observer's point of view.  
\item However, there is evidence that motor representation influences experience (e.g. acoustic experience of pitch direction).
\item One possibility: motor representation influences visual and acoustic experiences of movements and sounds, and these somehow facilitate goal ascription
\item This does not seem to be a fully adequate explanation because ?
\item Furthermore, motor representation enables experience which are (i) revelatory of action and (ii) distinct from visual or auditory experiences (Berti \&c).
\item So maybe: motor representation enables experiences of action as such
\item Conclusion: motor representation enables goal ascription by making possible experiences of action as such.  The role of motor representation in goal ascription is like the role of visual representation in judgements of motion.
\end{enumerate}

MR----> | acquisition| Action Judgment (action concept) <----> B \& D Judgment (b\&d concept)
tracking goal -----> || ascribing goal <----------------- > ascribing beliefs and desires

MR<----> Action Judgment (action concept) <----> B \& D Judgment (b\&d concept)

>>>>

The second step in our attempt to understand how some judgements depend on motor representations concerns the apparent isolation of motor representation from thought. When judgements about the goals of observed actions depend on the observers' motor representations, which processes connect motor representations to judgements?
We shall argue (in section \vref{sec:processes}) that motor representations are related to experiences.  There is a parallel between visual and motor representations. Visual representations of the particular colours of objects are related to experiences of those objects and their colours, and these experiences arguably provide reasons for judgements about the colours of objects.%
\footnote{
*Some controversy.  Campbell: yes; Davidson: no (experience plays a merely causal role).  We simply assume yes.  (Or we can duck: we're talking about appearance to the thinker of having reasons, not the fact of having reasons.)}
So the fact that visual representations enable judgements about particular colours in no way conflicts with the claim that thinkers have reasons for those judgements.  We shall argue that motor representations of outcomes are related to experiences of actions and their directedness to outcomes.  This is why thinkers can have reasons for judgements about the directedness of an action to a goal even where the judgements are enabled by motor representations---and also why it appears (veridically) to thinkers that they have such reasons.  Motor representation stands to experience of action as visual representation stands to experience of particular colours. This anyway is the view we shall defend.

@@

\section{Experience of Action}
\label{sec:processes}
How could motor representations sometimes have content-respecting influences on judgements about the goals of observed actions?  Broadly, our proposal is that the influence of motor representation on judgement goes via experience.  It is because motor representations sometimes influence our experiences when we observe actions that those motor representations can facilitate judgements about the actions.

Let us explain the idea in slightly more detail.  Observing actions sometimes involves \emph{experiences revelatory of action}, that is, experiences which provide the subject of experience with reasons for judgements about which action someone is performing. Suppose, for instance, that you are observing a stranger who you have never communicated with.  You may be able to judge, on the basis of observation that the stranger is walking a dog or gasping a cane.  You are able to make such judgements about the stranger's actions because your experiences provide you with reasons for them.

We claim that some experiences revelatory of action depend on motor representations of outcomes, and in such a way that which actions the experiences reveal is determined, at least in part, by which outcomes are represented motorically. This is what explains how motor representation sometimes has a content-respecting influence on judgement.  Our aim in  this section is to defend this claim about how experience depends on motor representation.  Defending this claim involves several steps.

The first step is to note that motor processes can influence visual processes.  For instance, \citet{bortoletto:2011_action} show that motor plans, such as might be involved in producing a gesture with the hand, can influence visual processes. Here the influence of motor representations on visual processes varies depending on both the gesture being planned and the visual stimulus presented. Importantly, these influences can be detected before any action occurs, showing that it is the motor representations rather than any consequent movements which are influencing visual processes.%
\footnote{
For a recent review of some of the evidence concerning motor influences on perceptual processing, see \citet{halasz:2012_unconscious}. (*refs)
}  
Of course, this evidence does not show that motor representation influences experience. After all, it may be possible to influence visual processes in ways that make no difference to experience.  But the evidence is relevant to our argument because if motor and perceptual processes did not interact at all, it might be reasonable to doubt that what is experienced can sometimes be determined, at least partly, by the contents of motor representations.

Next consider evidence that motor representation can influence perceptual judgement.  For some very special pairs of tones, the first is sometimes perceived as lower in pitch than the second and sometimes as higher in pitch.  Call these \emph{ambiguous tone pairs}.  Repp and Knoblich (\citeyear{repp:2007_action}) had a group of expert pianists and a control group of non-experts press two keys in sequence, where the first key was sometimes to the left, and sometimes to the right, of the second key.  The key presses produced an ambiguous tone pair, and the tones always occurred in the same order regardless of which key was pressed first.  By asking subjects to report how they perceived the relative pitch of the tones, Repp and Knoblich found that, for the expert pianists, the direction of the key presses influenced the perceived direction of the change in pitch. Could what influences perceptual experience in this case be not a motor representation but the occurrence of a movement, or perhaps even the perception of a movement of the subject's own fingers? Against this possibility, note that the effect was not observed in non-expert pianists: for them the direction of action did not measurably influence the perceived pitch direction. Since both groups moved in the same way, if the influence were due to movement only we would expect it to occur irrespective of expertise. Instead it seems likely that differences in expertise between the two groups of subjects, expert and non-expert, affected how the movements they performed were represented motorically, and that these differences in motor representation are in turn what explains their perception of relative pitch.  This study, and others like it,%
\footnote{
See also \citet{zwickel:2010_interference} who investigate effects of action on visual experience of motion.  *more \citep{schutz-bosbach:2007_perceptual}
}
provide relatively direct evidence that motor representation can influence perceptual experience.

There is a view about the control of action that may explain how motor representation sometimes influences perceptual experience.  In planning one's future actions it is sometimes useful to be able to predict the likely sensory consequences of actions currently being performed.  One can then treat these predictions as constraints and opportunities in planning what to do next.  Accordingly, motor representations of outcomes may be inputs to mechanisms that generate predicted sensory consequences. And these predictions may not only feed into planning but could also influence how the consequences of actions are experienced. So in Repp and Knoblich's experiment, it is possible that when the expert pianists plan sequences of key presses, it is predictions about the likely sensory consequences of their actions which bias them to perceive the ambiguous tone pair one way or another.

So far we have seen that motor representations can influence what is experienced.  Our aim is to show, further, that some of these experiences are revelatory of action, and that the influences are such that the contents of motor representations determine, at least partly, which actions the experiences reveal. How might this work?  Consider observing someone playing two notes on a piano.  Judging which action they are performing may be difficult as your view may be partially obscured and you may be too far away to see exactly what is happening.  But given that you know something about which sounds are produced by various piano playing actions, hearing the relative pitches of these notes might in principle assist you in recognizing that a goal of her action is to play these two notes.  So if, as the findings indicate, motor representation can influence perceptions of pitch, it might thereby indirectly facilitate judgements about the goals of actions.

For another illustration, suppose that an observer can associate the characteristic sound of a newspaper being snapped open with the action of snapping open a newspaper. Suppose also that, when observing an action, motor  representations can influence whether, when or how this observer experiences this characteristic sound.  Then motor processes can indirectly influence the speed and accuracy of the observer's judgements about which actions are directed to this goal, the snapping open of a newspaper, by influencing whether, when or how she experiences the characteristic sound of this action.

So far we have been considering experiences of characteristic sensory effects of actions. But experiences revelatory of action also include experiences of bodily configurations and movements as an action unfolds. [Ref exp Prinz and point lights]  These experiences may also be influenced by motor representations of outcomes.  As Wilson and Knoblich (\citeyear{Wilson:2005qu}, p.\ 463) suggest, occlusion and other factors mean that observers typically have limited perceptual information about agents' bodies and movements: motor representation in action observation may usefully enable observers `to fill in missing or ambiguous information'.

Here, then, is a proposal---call it the Indirect Hypothesis---about how the contents of motor representations partially determine which actions are revealed in experience (see also figure \vref{fig_indirect_hypothesis}).  In observing action, motor representation can influence perceptual experiences.  The relevant experiences are of bodily configurations and movements as an action unfolds, and of sensory effects of characteristic particular actions.  Such experiences sometimes enable an observer to make judgements about the goals of actions, for she may associate particular patterns of bodily movement or particular sensory effects with particular goals.  But in many cases of action observation, the agent's bodily movements and the sensory effects of her actions are partially obscured or surrounded by irrelevant distractors, or otherwise difficult to identify.  But, as we have seen, there is evidence that motor representation can influence such experiences of bodily configurations and movements, and of sensory effects.  Motor representations could thereby facilitate judgements about the goals of actions.  So it is possible that motor representations sometimes enhance perceptual experiences of movements or sensory effects which in turn sometimes facilitate judgements about the goals of actions.%
\footnote{
The Indirect Hypothesis is inspired by and consistent with views defended in \citet{Csibra:2007fy} and \citet{Wilson:2005qu}.  However, to our knowledge these authors have not considered  our question about content-respecting influences of motor representation on judgement, and we are not suggesting that the would endorse the Indirect Hypothesis in its entirety.  
}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{fig_indirect_hypothesis.png}
\caption{
\label{fig_indirect_hypothesis}
	The Indirect Hypothesis.
}
\end{center}
\end{figure}

A possible objection to the Indirect Hypothesis is that the evidence we have considered leaves open the question of how extensive the influence of motor representations on perceptual experiences of bodily configurations, movements and the sensory effects of actions is.  For all we have said, such influences may be rare.  This is a potential problem for our attempt to use the Indirect Hypothesis to explain how motor representations have content-respecting influences on judgements.  The Indirect Hypothesis does provide a theoretically coherent and empirically motivated explanation of how such influences are possible in principle. But currently available evidence does not allow us to determine whether the Indirect Hypothesis can explain every case in which a motor representations has a content-respecting influence on a judgement.  Perhaps there is more to the story.

\section{Motor Experience}
Our question is how motor representations could have a content-respecting influence on judgements about the goals of actions.
The answer, we suppose, must involve a relation between motor representation and experience.
In the previous section we defended the hypothesis that motor representations of outcomes to which actions are directed influence perceptual experiences of the agents' bodies and movements in ways that facilitate judgements about the goals of the actions. 
But this hypothesis may not be the whole story about experience of action.
In this section we discuss a more radical hypothesis---call it the Direct Hypothesis---about how the contents of motor representations can influence what we experience when we observe actions.

The Direct Hypothesis starts from the premise that in observing action we experience not only bodily configurations, movements, sounds and the rest but also goal-directed actions as such . Such experiences---call them motor experiences---stand to motor representations somewhat as visual experiences stand to visual representations.  So motor representations can have a content-respecting influence on judgements because motor representations enable motor experiences on which the judgements can be  based.  Or so the Direct Hypothesis claims 
(see figure \vref{fig_direct_hypothesis}).%
\footnote{
In formulating the Direct Hypothesis we draw on ideas from \citet{rizzolatti_mirrors_2008} and \citet{Jeannerod:1999kj}.
}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{fig_direct_hypothesis.png}
\caption{
\label{fig_direct_hypothesis}
	The Direct Hypothesis.
}
\end{center}
\end{figure}
